Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2021-12-27 paper.tex
Soften mixing statement and reword viscous heat generation phrase

\rev{We have found evidence of the flute instability using both models of
viscosity, however isotropic viscosity damps the initial growth such that it
does not develop beyond its linear phase before the faster growing kink
instability disrupts the flux tube and halts the development of the flute. Due
to the enhanced growth of the flute instability in the anisotropic case, the
tube becomes more readily mixed and the growth rate of the kink instability is
smaller. Beyond the effect on the growth of the two observed instabilities, the
two viscosity models greatly affect both the viscous heating and Ohmic heating
rates. Anisotropic viscosity is naturally less dissipative than isotropic
viscosity and results in viscous heating approximately two orders of magnitude
less than that associated with isotropic viscosity. This is somewhat offset by
the anisotropic viscosity model permitting greater kinetic energy release and
enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
generation of small, strong current sheets. The overall effect is that more
heat is released when the viscosity is anisotropic. This is similarly observed
in previous work~\citep{quinnEffectAnisotropicViscosity2020}.}

@@

Our set of numerical experiments has shown that the mixing as a result of the
nonlinear flute instability appears to slow the growth of the kink instability.
It seems unlikely that in the linear regime the perturbations of the flute and
kink are able to directly couple, given that the kink instability generally
presents at the axis of a flux tube and the flute at some resonant surface away
from the axis. Further investigation of the nonlinear interaction between the
two instabilities is required.

>>>>

\rev{We have found evidence of the flute instability using both models of
viscosity, however isotropic viscosity damps the initial growth such that it
does not develop beyond its linear phase before the faster growing kink
instability disrupts the flux tube and halts the development of the flute. Due
to the enhanced growth of the flute instability in the anisotropic case, the
tube becomes more readily mixed and the growth rate of the kink instability is
smaller. Beyond the effect on the growth of the two observed instabilities, the
two viscosity models greatly affect both the viscous heating and Ohmic heating
rates. Anisotropic viscosity is naturally less dissipative than isotropic
viscosity and generates approximately two orders of magnitude less total
viscous heat than isotropic viscosity. This is somewhat offset by the
anisotropic viscosity model permitting greater kinetic energy release and
enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
generation of small, strong current sheets. The overall effect is that more
heat is released when the viscosity is anisotropic. This is similarly observed
in previous work~\citep{quinnEffectAnisotropicViscosity2020}.}

@@

Our set of numerical experiments has suggested that the mixing as a result of the
nonlinear flute instability slows the growth of the kink instability.
It seems unlikely that in the linear regime the perturbations of the flute and
kink are able to directly couple, given that the kink instability generally
presents at the axis of a flux tube and the flute at some resonant surface away
from the axis. Further investigation of the nonlinear interaction between the
two instabilities is required.
